%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{发表文章}

	\textbf{Huiyao Zhang}. (2025). An Efficient Framework for Aerial Object Detection via Enhanced Feature Fusion and
	Localization Quality Estimation. \textit{IEEE Access}, \textbf{under review}
    
	\textbf{Huiyao Zhang}. (2025). DroneDetect: Multiscale Feature Fusion and Attention-Driven Architecture for UAV Object
	Detection. \textit{Journal of Advanced Computational Intelligence and Intelligent Informatics}. \textbf{SCI, third review} 

	\textbf{Huiyao Zhang}. (2025). HarmoNet: Balancing Computational Efficiency and Detection Accuracy for Drone-Based Object
	Recognition. \textit{International Journal of Pattern Recognition and Artificial Intelligence}. \textbf{SCI, accept} 

	\textbf{Huiyao Zhang}. (2025). AeroYOLO: Efficient Multiscale and Attention-Augmented YOLOv8s for Robust Aerial Object
	Detection. \textit{IEEE Access}. 13:163143-163161. DOI:10.1109/ACCESS.2025.3610617.\textbf{SCI}

	\textbf{Huiyao Zhang}, Yuxiao Wang, Fangmeng Zeng. (2022). The Multi-Objective Design of Laminated Structure with
	Non-Dominated Sorting Genetic Algorithm. \textit{International Journal of Advanced Computer Science and
	Applications}.  DOI: 10.14569/IJACSA.2022.01310106.\textbf{EI}

	\textbf{Huiyao Zhang}, Atsushi Yokoyama. (2022). Optimum Design of Laminated Composites for Minimum Thickness by a
	Variant of Genetic Algorithm. \textit{Journal of Textile Engineering}. DOI:10.4188/jte.68.31. \textbf{EI}
	
	\textbf{Huiyao Zhang}, Atsushi Yokoyama. (2021). A Technique for Constrained Optimization of Cross-ply Laminates
	Using a New Variant of Genetic Algorithm. \textit{International Journal of Advanced Computer Science and
	Applications}, 12(6): 760-767. DOI:10.14569/IJACSA.2021.0120689. \textbf{EI}

	\textbf{Huiyao Zhang}, Atsushi Yokoyama. (2021). Predicting Strength Ratio of Laminated Composite Material with
	Evolutionary Artificial Neural Network. \textit{International Journal of Advanced Computer Science and
	Applications}, 12(6): 11-18. DOI:10.14569/IJACSA.2021.0120602. \textbf{EI}

	\textbf{Hui-Yao Zhang}, Duan Li, Hao-Yang Xie, Yue-Qi Zhong. (2017).  A Study on the Female Chest Contour with
	Elliptic Fourier Analysis. \textit{Journal of Fiber Bioengineering and Informatics}, 10(3): 131-139. DOI:
	10.3993/jfbim00268. \textbf{ISTP}

	\textbf{Hui-Yao Zhang}, Duan Li, Hao-Yang Xie, Yue-Qi Zhong. (2017).  Elliptic Fourier Analysis on Female Chest
	Contour. Textile Bioengineering and Informatics Symposium. \textbf{ISTP}

